R dyntrace report

### 2018-03-23 graphs/report.Rmd
Trace without compiling.wq

@@

``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.position="none")
)
```

>>>>

aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print

@@

``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
#make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
#  ggplot(data, aes(x=type, y=percent)) +
#    geom_violin(draw_quantiles = c(.25, .5, .75)) +
#    scale_y_continuous(labels=pp_perc) +
#    theme(axis.title.x=element_blank(), 
#          axis.title.y=element_blank(), 
#          legend.position="none")
#)
```
